Refinements for Open Automata

### 2023-06-21 2021-Refinement/paper/refinementarticleV2.tex
minor

\begin{proofsketch}
% TODO: I don't understand this definition, why v = v on vars(s1), what about s2
% ANS: was copy paste from the report, polished now
The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\). This is shown  by considering the relation $\mathcal{R}$ such that $\mathcal{R}\mpar{s_1, s_2} \triangleq s_1=s_2\land \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$   we can prove the conditions for Definition~\ref{Def:OA-Refinement}.
%
%\begin{theorem}[Transitivity]
%If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
%\end{theorem}
Appendix~\ref{sec:proof-transitivity} presents the proof of transitivity. It is done classically by identifying the relation between $A_1$ and $A_3$ that is a simulation. What is less classical is the definition of this relation because it is a boolean formula. For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a  formula that defines the simulation. To do this, we take the disjunction of formulas relating $s_1$ and $s_3$, and passing by all states $s_2$ of $A_2$. More precisely, we define a relation of the following form:
  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
We then prove that this relation  is a simulation, according to Definition~\ref{Def:OA-Refinement}.
\end{proofsketch}

>>>>

\begin{proofsketch}
% TODO: I don't understand this definition, why v = v on vars(s1), what about s2
% ANS: was copy paste from the report, polished now
The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\). This is shown  by considering the relation $\mathcal{R}$ such that $\mathcal{R}\mpar{s_1, s_2} \triangleq s_1=s_2\land \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$   we can prove the conditions for Definition~\ref{Def:OA-Refinement}.
%
%\begin{theorem}[Transitivity]
%If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
%\end{theorem}
Appendix~\ref{sec:proof-transitivity} presents the proof of transitivity. It is done classically by identifying the relation between $A_1$ and $A_3$ that is a simulation. What is less classical is the definition of this relation because it is a boolean formula. For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a  formula that defines the simulation. To do this, we take the disjunction of formulas relating $s_1$ and $s_3$, and passing by all states $s_2$ of $A_2$. More precisely, we define a relation of the following form:
  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land \mathcal{R}_{23}(s_2,s_3) } \]
We then prove that this relation  is a simulation, according to Definition~\ref{Def:OA-Refinement}.
\end{proofsketch}
